---
title: "Elsevier"
author: "Prayag Gordy"
date: "5/25/2022"
output: pdf_document
documentclass: elsarticle
classoption: preprint
bibliography: references.bib
nocite: '@*'
csl: apa.csl
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
```

## Citations

**Keep in mind that all citations in this document are arbitrary.**

There are so many options [@js61]! We can easily cite at the beginning of sentences and with page numbers. @fb94[p.33] wants us to include one additional citation. The information in each citation is easy to change in the `.bib` file, says Foo Bar [-@fb94].

## Plots and tables

Let's include a plot. Quality isn't an issue since it renders with the pdf (for example, zoom in on the axis text—you'll see no reduction in quality):

```{r fig.cap="A simple plot with mtcars"}
ggplot2::ggplot(mtcars, ggplot2::aes(x = disp, y = mpg)) + ggplot2::geom_point()
```

And now, for a table:

```{r}
kableExtra::kable_styling(knitr::kable(mtcars[,c("mpg", "cyl", "disp")], caption = "Nice table!", booktabs = T), latex_options = c("hold_position"))
```

## Creating the RMD

Creating this RMD is quite simple. Download the CLS from Elsevier and unzip into the project directory. Then, add your `bib`
and `csl` files into the project directory. Include the `documentclass`, `bibliography`, and `csl` tags in the YAML header, along with optional tags such as `classoption` and `nocite`.

# References

